Sparse Function-space Representation \\ of Neural Networks

### 2023-05-14 paper/main.tex
updatedd
update section intro

In this section, we recap how a function-space posterior -- a GP posterior -- can be obtained
by linearising a neural network around the Maximum a Posteriori (MAP) weights.

>>>>

In this section, we recap how a trained neural network (NN) can be converted to a Gaussian process by locally linearising
its weights.
% a GP posterior -- can be obtained
% around the Maximum a Posteriori (MAP) weights.

% by linearising a neural network around the Maximum a Posteriori (MAP) weights.
% a GP posterior -- can be obtained
